Measuring and optimizing machine learning interpretability

### 2019-03-20 2019-03-21-dagstat-imlm/dagstat-molnar.Rmd
fix some errors

```{r, echo = FALSE}
knitr::include_graphics("../images/black-box.png")
```
## Problem: Tradeoff interpretability and performance
Use only interpretable models (e.g. linear model)!

$\Rightarrow$ Pay with loss in performance.

```{r, echo = FALSE}
knitr::include_graphics("../images/white-box.png")
```
## Problem: Tradeoff interpretability and performance
Just use post-hoc interpretation methods (e.g. feature importance)!

$\Rightarrow$ Works better for less complex models.

@@

## What's interpretability anyway?

@@

## We propose measures of model complexity

@@

$$\text{Interaction Strength} =  \frac{\mathbb{E}(L(\hat{f}, f_0 + \sum_{j=1}^p f_j)}{\mathbb{E}(L(\hat{f}, c))}$$

@@

- Predict wine quality from phsicochemical properties
- Minimize MAE, number of features, interaction strength, main effect complexity
- Search across different model classes and hyperparameter settings

>>>>

```{r, echo = FALSE}
knitr::include_graphics("../images/black-box.png")
```
## Solution: Interpretable Models?

$\Rightarrow$ Pay with loss in performance; Unclear how to compare models

```{r, echo = FALSE}
knitr::include_graphics("../images/white-box.png")
```
## Solution: Post-hoc Interpretation?

$\Rightarrow$ Post-hoc interpretation (e.g. feature importance, partial dependence plots) works better for less complex models.

@@

## Is Interpretability Unscientific?

@@

## We Propose Measures of Model Complexity

@@

$$\text{Interaction Strength} =  \frac{\mathbb{E}(L(\hat{f}, f_0 + \sum_{j=1}^p f_j))}{\mathbb{E}(L(\hat{f}, c))}$$

@@

- Predict wine quality from physicochemical properties
- Minimize MAE, number of features, interaction strength, main effect complexity
- Search across different model classes and hyperparameter settings
